Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/simulation.tex
Minor edits and clean up.

\begin{figure}
%\centering
\begin{subfigure}[b]{0.25\textwidth}
\centering
\includegraphics[width=1.5in]{../figs/synthetic/mat.pdf}
\end{subfigure}
~
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=2in]{../figs/synthetic/counts.pdf}
\end{subfigure}
~
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=2.5in]{../figs/synthetic/params-estimates.pdf}
\end{subfigure}
\caption{[TODO: Remove AB-XA, etc from the plot. Rotate them. Use subfigure labels.] Illustration of 2000 simulated events, as described in text. Left: Counts of each dyad. Center: Boxplot of distribution of participation counts across dyads.  The top left shows an increased propensity for reciprocity within cluster 1; bottom right shows more AB-AY events within cluster 2.  Right: Parameters (in red) and posterior credible intervals (in black).}
\label{fig:syncounts}
\end{figure}

\section{Simulation}

>>>>

\begin{figure}
%\centering
\begin{subfigure}[b]{0.25\textwidth}
\centering
\includegraphics[width=1.5in]{../figs/synthetic/mat.pdf} %counts2.pdf
\vspace{.25cm}
\caption{}
\end{subfigure}
~
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=2in]{../figs/synthetic/counts.pdf}
\caption{}
\end{subfigure}
~
\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=2.1in]{../figs/synthetic/params-estimates.pdf}
\vspace{-.5cm}
\caption{}
\end{subfigure}
\caption{Illustration of 2000 simulated events, as described in text. (a) Counts of each dyad. (b) Boxplot of distribution of participation counts across dyads.  The top left shows an increased propensity for reciprocity within cluster 1; bottom right shows more AB-AY events within cluster 2.  (c) Parameters (in red) and posterior credible intervals (in black).}
\label{fig:syncounts}
\end{figure}

\section{Simulation}
\label{sec:simulation}
